\documentclass[11pt]{article} % Default font size is 12pt, it can be changed here

\usepackage{geometry} % Required to change the page size to A4
\geometry{a4paper} % Set the page size to be A4 as opposed to the
\begin{document}
Ask testers to complete either Scenario A or Scenario B. Afterwards, ask them them questions in Section \ref{sec:quest}.
\section{Scenario A}
Ask the user to find information on a Computer Science course.

Try to make the following observations
\begin{itemize}
    \item How long did it take them?
    \item Do they seem fustrated at any time?
    \item Did they seem confused at any time?
    \item Did they ever ask for help?
\end{itemize}
\section{Scenario B}
Ask the user to casually browse the website. Tell them to click on what interests them.

Try to make the following observations
\begin{itemize}
    \item Do they seem fustrated at any time?
    \item Did they seem confused at any time?
    \item How long did it take them to ask for help?
\end{itemize}
\newpage

\section{Questions}\label{sec:quest}
\begin{description}
    \item[1] How easy was it to find information? \newline\newline
    Hard \quad\quad 0\quad\quad\quad 1\quad\quad\quad 2 \quad\quad\quad 3 \quad\quad\quad 4 \quad\quad\quad 5\quad\quad Easy
    \newline
    \item[2] What do you think the sliders on the main page do? \newline\newline\newline
    \item[3] How easy was the layout on the search results page to understand? \newline\newline
Hard \quad\quad 0\quad\quad\quad 1\quad\quad\quad 2 \quad\quad\quad 3 \quad\quad\quad 4 \quad\quad\quad 5\quad\quad Easy\newline
    \item[4] How informative was the table page? \newline \newline  
Not informative \quad\quad 0\quad\quad\quad 1\quad\quad\quad 2 \quad\quad\quad 3 \quad\quad\quad 4 \quad\quad\quad 5\quad\quad Informative\newline
    \item[5] How attractive did you find the university main page? \newline\newline Not attractive \quad\quad 0\quad\quad\quad 1\quad\quad\quad 2 \quad\quad\quad 3 \quad\quad\quad 4 \quad\quad\quad 5\quad\quad Attractive\newline
    \item[6] If you could improve the site in any way, what would you do? \newline\newline\newline
    \item[7] Do you have any other comments?

\end{description}
\end{document}
